results notes

### 2022-09-01 RR_manuscript/results_notes.Rmd
add analyst team descriptives

library(brms)
library(faux)
library(dplyr)
library(ggplot2)
library(tidybayes)

@@

msa_models <- readRDS("./data/analyses/msa_models.rds") %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

# number of teams
no_teams = length(unique(msa_models$team))

@@

# Sample characteristics
In the following, we will describe the characteristics of our ananlyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.

@@

`r no_teams` teams initially signed up to participate. xx dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining xx teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

@@

meta_bm <- readRDS("./data/meta_analysis/meta_bm.rds")

@@

knitr::include_graphics("./plots/meta_plot1.png")

@@

knitr::include_graphics("./plots/alltogether.png")

>>>>

library(brms)
library(faux)
library(dplyr)
library(ggplot2)
library(tidybayes)
library(here)

@@

msa_models <- readRDS(here("./data/analyses/msa_models.rds")) %>%
  mutate(
    outcome = as.factor(outcome),
    typicality = as.factor(typicality),
    temporal_window = as.factor(temporal_window)
  ) %>%
  droplevels() %>%
  mutate(
    outcome = contr_code_sum(outcome),
    typicality = contr_code_sum(typicality),
    temporal_window = contr_code_sum(temporal_window)
  )

@@

# number of teams (final)
no_teams = length(unique(msa_models$team))

# number of teams (initially)
no_teams_init <- readr::read_csv(
  here::here("data", "questionnaires", "msa_intake_form.csv")) %>% 
  select(Q6) %>% # Questions asking for team leader
  filter(!(row_number() %in% c(1, 2))) %>% 
  distinct() %>% 
  nrow

@@

# Sample characteristics

In the following, we will describe the characteristics of our analyst teams and their models in order to give an overview over the sample and the large variation across analysis strategies.

@@

`r no_teams_init %>% xfun::numbers_to_words() %>% stringr::str_to_title()` teams initially signed up to participate. 
`r (no_teams_init - no_teams) %>% xfun::numbers_to_words() %>% stringr::str_to_title()` of the proposed teams dropped out of the project during the analysis phase^[ADD REASONS]. 
The remaining `r no_teams` teams submitted their analysis in time and were coded by the three initiating authors (SC, JC, TR).

@@

meta_bm <- readRDS(here("./data/meta_analysis/meta_bm.rds"))

@@

knitr::include_graphics(here("./plots/meta_plot1.png"))

@@

knitr::include_graphics(here("./plots/alltogether.png"))
